---
title: "Exercise 2"
output: html_document
---

# Exercise 2. Networks

#
#


### Daniel H. Vedia Jerez
### Luís Sastre San Emeterio

#
#

#### 1 & 2) Enter it as a graph G & connecting nodes A and F

```{r setup, include = FALSE}

library(igraph)          # load a package

## 1 & 2) Enter it as a graph G & connecting nodes A and F
G00 <- graph(edges=c('D','C','G','D','G','F','F','C','D','B','H','F','E','A','H','E',
                   'C','B' ), directed=F) 
plot(G00, vertex.color="gold", vertex.size=15, 
     vertex.frame.color="gray", vertex.label.color="black", 
     vertex.label.cex=1.5, vertex.label.dist=2, edge.curved=0.2)
```

```{r}
plot(G00)
```

Connection nodes A & F

```{r , include = FALSE}
G <- graph(edges=c('D','C','G','D','G','F','F','C','D','B','H','F','E','A','H','E','F'
                   ,'A','C','B' ), directed=F) 
plot(G, vertex.color="gold", vertex.size=15, 
     vertex.frame.color="gray", vertex.label.color="black", 
     vertex.label.cex=1.5, vertex.label.dist=2, edge.curved=0.2)
```

```{r}
plot(G)
```

#### 3 & 4) Obtain its vectors of edges and nodes of graph G

```{r}
E(G)
V(G)
```

#### 5) graph H from this adjacency matrix

```{r}
am <- as_adjacency_matrix(G)
```
```{r, include=FALSE} 
H <- graph_from_adjacency_matrix( am, mode = 'undirected' )
plot(H, vertex.color="yellow", vertex.size=15, 
     vertex.frame.color="gray", vertex.label.color="black", 
     vertex.label.cex=1.5, vertex.label.dist=2, edge.curved=0.2)
```

```{r}
plot(H)
```

#### 6) Find the order, the size and the density of G
```{r}
gorder(G)
gsize(G)
edge_density(G, loops = FALSE)
```

#### 7) Find the largest degree of nodes in G.
```{r}
max.deg <- degree(G, mode="all")
plot(G, vertex.size=45)
hist(max.deg, breaks=1:vcount(G)-1, main="Histogram of node degree", col='green')
```

#### 8)  A directed graph G0 from the graph in Figure 1
```{r}
G0 <- graph(edges=c('C','D','D','G','G','F','C','F','B','D','F','H','A','E','E','H','A'
                   ,'F','B','C' ), directed=TRUE) 
plot(G0)
```

#### 9) Obtain its vectors of arcs and nodes of grapg G0

```{r}
E(G0)
V(G0)
```

#### 10) Obtain the adjacency matrix of G0.
```{r}
am0 <- as_adjacency_matrix(G0)
```

#### 11) Deleting node D &  add to it new arcs between its neighbors

```{r}
g10 <- graph_from_literal(c-+d:h+-g:g+-c, a-+e-+h+-d+-b-+c)
plot(g10)
```

#### 12) Simplify it and plot it again & call it G1

Deleting nodes A & G to simplify the Graph G10

```{r}
G1 <- simplify(g10, remove.multiple = TRUE, remove.loops = TRUE)
plot(G1)
```

#### 13) Find the largest degree of nodes in G1.
```{r}
max.deg1 <- degree(G1, mode="all")
plot(G1, vertex.size=40)
hist(max.deg1, breaks=1:vcount(G1)-1, main="Histogram of node degree", col = 'orange')
```

